Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-10 article.tex
expanded discussion of axioms regarding boundary cases of windows of range 0 and at instant 0

{\nobreak\begin{axiom}\label{axiom:continuous datalog: window range leq 0}
A window of range $0$ over a stream $S$ at an instant 
${i \in \mathbb{T}}$ is always empty.
\begin{equation*}
W^{S,0}_{i} = \varnothing
\end{equation*}
\end{axiom}}

{\nobreak\begin{axiom}\label{axiom:continuous datalog: window start leq 0}
A window of any range $x \in \mathbb{N}$ over a stream $S$ at (or before)
the first instant of time is always empty.
\begin{equation*}
W^{S,x}_{i} = \varnothing
\end{equation*}
where $i \leqslant 0$.
\end{axiom}}

@@

{\nobreak\begin{axiom}\label{axiom:continuous datalog: window disjointness}
A window of range ${x \in \mathbb{N}}$ over a stream $S$ at an
instant ${i \in \mathbb{T}}$ is disjoint from a second window of 
range ${y \in \mathbb{N}}$ over $S$ at any instant before $i - x$.
\begin{equation*}
W^{S,x}_{i} \cap W^{S,y}_{i-z} = \varnothing
\end{equation*}
where $z \geqslant x$.
\end{axiom}}

>>>>

{\nobreak\begin{axiom}\label{axiom:continuous datalog: window range leq 0}
The state of a window of range $0$ over a stream $S$ at an instant 
${i \in \mathbb{T}}$ is always empty.
\begin{equation*}
W^{S,0}_{i} = \varnothing
\end{equation*}
\end{axiom}}

Axiom \ref{axiom:continuous datalog: window range leq 0} is trivially
true by reference to the interval in \refdef{continuous datalog: window},
and the definition of numeric intervals.  The state of a window of range
$0$ over stream $S$ at interval $i$ is composed of fact instances that
are each mapped by $S$ to any instant in the interval ${(i,i]}$.  This
interval is defined as the set of numbers ${\{ x \mid i < x \leqslant i \}}$,
which is the empty set for any $i$.

{\nobreak\begin{axiom}\label{axiom:continuous datalog: window start leq 0}
A window of any range $x \in \mathbb{N}$ over a stream $S$ at the
first instant of time is always empty.
\begin{equation*}
W^{S,x}_{0} = \varnothing
\end{equation*}
\end{axiom}}

Axiom \ref{axiom:continuous datalog: window start leq 0} follows from
Axiom \ref{axiom:continuous datalog: window range leq 0} and the definition
of the $-$ operator with regards to instants in
\refdef{continuous datalog: instant}.  The state of a window of range
$x$ over stream $S$ at the first interval is composed of fact instances that
are each mapped by $S$ to any instant in the interval ${(0-x,0]}$. As the instant
${0 - x = 0}$, the interval of instants in $W^{S,x}_{0}$ evaluates to ${(0,0]}$,
which makes it empty by Axiom \ref{axiom:continuous datalog: window range leq 0}.

@@

{\nobreak\begin{axiom}\label{axiom:continuous datalog: window disjointness}
A the state of a window of range ${x \in \mathbb{N}}$ over a stream $S$ at an
instant ${i \in \mathbb{T}}$ is disjoint from a second state of any window of 
range ${y \in \mathbb{N}}$ over $S$ at any instant before $i - x$.
\begin{equation*}
W^{S,x}_{i} \cap W^{S,y}_{i-z} = \varnothing
\end{equation*}
where $z \geqslant x$.
\end{axiom}}
